\documentclass[a4paper,10pt]{article}
\usepackage[margin=15mm]{geometry}
\usepackage{pgf,tikz}
\usepackage{algorithm2e}
\usepackage{subfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage{amssymb}
\usepackage{noweb}
\usepackage{listings}
\usetikzlibrary{circuits.logic.US}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
 
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{ %
  language=Verilog,                % the language of the code
  basicstyle=\footnotesize,           % the size of the fonts that are used for the code
  numbers=left,                   % where to put the line-numbers
  numberstyle=\tiny\color{gray},  % the style that is used for the line-numbers
  stepnumber=2,                   % the step between two line-numbers. If it's 1, each line 
                                  % will be numbered
  numbersep=5pt,                  % how far the line-numbers are from the code
  backgroundcolor=\color{white},      % choose the background color. You must add \usepackage{color}
  showspaces=false,               % show spaces adding particular underscores
  showstringspaces=false,         % underline spaces within strings
  showtabs=false,                 % show tabs within strings adding particular underscores
%  frame=single,                   % adds a frame around the code
  rulecolor=\color{black},        % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. commens (green here))
  tabsize=2,                      % sets default tabsize to 2 spaces
  captionpos=b,                   % sets the caption-position to bottom
  breaklines=true,                % sets automatic line breaking
  breakatwhitespace=false,        % sets if automatic breaks should only happen at whitespace
  title=\lstname,                   % show the filename of files included with \lstinputlisting;
                                  % also try caption instead of title
  keywordstyle=\color{blue},          % keyword style
  commentstyle=\color{dkgreen},       % comment style
  stringstyle=\color{mauve},         % string literal style
  escapeinside={\%*}{*)},            % if you want to add LaTeX within your code
  morekeywords={*,...}               % if you want to add more keywords to the set
}
\usepackage{amsthm}
\usepackage{hyperref}
\setlength{\parskip}{3mm}
\newtheorem{axiom}{Axiom}
\newtheorem{definition}{Definition}
\newtheorem{comment}{Comment}
\newtheorem{example}{Example}
\newtheorem{lemma}{Lemma}
\newtheorem{prop}{Property}
\newtheorem{problem}{Problem}
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}

% Title Page
\title{EE677 : \textbf{Foundation of VLSI CAD} \\
Comments on project problems}
\author{Dilawar Singh}
\date{Sep 22, 2012}

\begin{document}
\maketitle

\begin{abstract}

  This document partly describes many of the problems listed on course wiki.
  This is not a technical document which explains problems in details.
  Algorithms used to tackle these problems can be found in two books :
  \textbf{Introduction to algorithms}, Cormen, Leiserson et. al.  which deals
  with algorithms in general; and \textbf{Graph Theory} with application to
  Engineering and Computer Science by Narsing Deo, which explains graph
  algorithms lucidly.

  Algorithms related with placement and routing, circuit partitioning, layout
  generation in the area of VLSI CAD can be found in \textbf{VLSI Physical
  Automation} by Sadiq M Sait et. al.. 

  It is hard to say how much effort is precisely needed to solve problems listed
  in this document. It depends as much on your fluency with programming language
  as it depends on theoretical understanding. However, I have mentioned an
  integer in front of some problems which roughly indicates the effort needed to
  solve them. Needless to say, this number can be well wide off the mark.

\end{abstract}

\include{datastructures}
\include{boolean}
\include{vlsi}
\include{automata}

\end{document}          
